### 2013-08-04 inst/doc/one-simple-way.Rmd
writing continues, various edits

@@

4) warnings about known problems or inconsistencies in the data, and 
5) information to check that the data are properly imported, such as the number of rows and columns in the dataset and the total sum of numerical columns

@@

The second file provides the unprocessed data as a .csv file

>>>>

Sharing is as easy as `publish_reml("my_eml_data.xml")`

@@

> 4) warnings about known problems or inconsistencies in the data, and 
> 5) information to check that the data are properly imported, such as the number of rows and columns in the dataset and the total sum of numerical columns

@@

The second file provides the unprocessed data as a `.csv` file.  Because `csv` file formats vary
